This is an example of article title

### 2024-09-03 paper/paper.tex
Increase legend of Fig. 2
Updated the perspectives section

%- General peridynamics context
Peridynamics is a nonlocal continuum mechanics formulation, which was invented by Silling \cite{Silling2000}.
It has gained increased popularity as an approach for modeling fracture.
The deformation of the solid is described by integro-differential equations that are also fulfilled for discontinuities, making it very capable of modeling crack propagation and fragmentation with large displacements.
Much peridynamics research has been done in recent years, summarized in various review papers and books \cite{Diehl2019,Javili2019Review,Madenci2014}.

@@

\begin{figure}
\centerline{\includegraphics[width=0.8\linewidth]{tensile_test.png}}
\caption{Fracture simulation of tensile tension test with a crack propagating in the middle of the specimen}
\label{fig:tensiletest}
\end{figure}

@@

\section{Perspectives}
In version \texttt{0.2.0}, a multithreading approach is employed.
An extension to a hybrid approach utilizing MPI and multithreading is currently underway and is planned for version \texttt{0.3.0}.
The internals have been thoroughly reworked to incorporate a parallel data structure, resulting in significantly faster simulations that surpass the performance of \texttt{Peridigm}.
The planned changes include new material models and a simplified API with streamlined internal structures.

>>>>

%- General peridynamics context
Peridynamics is a nonlocal continuum mechanics formulation, which was introduced by Silling \cite{Silling2000}.
It has gained increased popularity as an approach for modeling fracture.
The deformation of the solid is described by integro-differential equations that are also fulfilled for discontinuities, making it very capable of modeling crack propagation and fragmentation with large displacements.
Much peridynamics research has been done in recent years, summarized in various review papers and books \cite{Diehl2019,Javili2019Review,Madenci2014}.

@@

\begin{figure}
\centerline{\includegraphics[width=0.9\linewidth]{tensile_test.png}}
\caption{Fracture simulation of tensile tension test with a crack propagating in the middle of the specimen}
\label{fig:tensiletest}
\end{figure}

@@

\section{Perspectives}
In version \texttt{v0.2.0}, a multithreading approach is employed.
An extension to a hybrid approach with MPI or multithreading is made in version \texttt{v0.3.0}.
The internals have been thoroughly reworked to incorporate a data structure that can be used for parallel simulations with either MPI or multithreading.
These changes also include new material models and a simplified API with streamlined internal structures.
For future versions it is planned to add improved material models and to utilize \texttt{DifferentialEquations.jl} for the time integration.
